Can the symmetric \textit{Fermi} and eROSITA bubbles be produced by tilted jets?

### 2022-05-11 paper.tex
update

%\item The clumpiness of the ISM disk has an insignificant impact on the\
%      overall dynamic of the Galactic bubbles.\
%      The development of the reverse shocks (the innermost bubbles) is always
%      associated with the dense disk,\
%      without the disc, only asymmetric forward shocks exist.
%      {\color{red} KY: I removed the second point about the innermost bubbles for now, because I think the following two points should be separated: (1) inclusion of the disk is critical for forming symmetric Galactic bubbles, (2) we found a pair of innermost bubbles which are reverse shocks (and perhaps comment on their properties and/or observable signatures). PH: done! }
\item The development of the expanding forward-reverse shock pair is always associated with the dense disk.
%the dense disk, although the clumpiness of the disk has an insignificant impact on the\
%overall dynamic of the Galactic bubbles.
%Furthermore,
In the absence of the disk, only forward shocks are present,
indicating the inclusion of the disk is critical for forming the innermost bubbles.

@@

\item The edge of the eROSITA bubbles is a forward shock,
      originally driven by bipolar jets emanating from the GC around 12 Myr ago
      for a duration of 1.2 Myr,
      and significantly expanded in the stratified atmosphere afterwards.

@@

      increasing the compressibility of the fluid and enhancing the thermal Bremsstrahlung emissivity

@@

\item Assuming a leptonic model with a spatially uniform, power-law CRe spectrum
      ranging from 0.5 MeV to 562.1 GeV, we showed that the observed gamma-ray and microwave spectra

@@

\item The elapsed time of 12 Myr is required for the simulated bubbles to reach the desired morphology.

@@

\item The Galactic bubbles are nearly symmetric about the Galactic plane albeit\

@@

      which release the caveat of earlier jet models where jets need to be vertical.

>>>>

%\item The clumpiness of the ISM disk has an insignificant impact on the\
%      overall dynamic of the Galactic bubbles.\
%      The development of the reverse shocks (the innermost bubbles) is always
%      associated with the dense disk,\
%      without the disc, only asymmetric forward shocks exist.
%      {\color{red} KY: I removed the second point about the innermost bubbles for now, because I think the following two points should be separated: (1) inclusion of the disk is critical for forming symmetric Galactic bubbles, (2) we found a pair of innermost bubbles which are reverse shocks (and perhaps comment on their properties and/or observable signatures). PH: done! }
\item The development of the expanding forward-reverse shock pair is always associated with the dense disk.
%the dense disk, although the clumpiness of the disk has an insignificant impact on the\
%overall dynamic of the Galactic bubbles.
%Furthermore,
In the absence of the disk, the reverse shock is absent,
indicating the inclusion of the disk is critical for forming the innermost bubbles.

@@

\item eROSITA bubbles coincide with the forward shock front
      originally driven by short-lived bipolar jets
      for a duration of 1.2 Myr, where the bubbles later significantly
      expanded into the stratified atmosphere to reach the present 12kpc height.

@@

      increasing the compressibility of the fluid and
      enhancing the thermal Bremsstrahlung emissivity

@@

\item Assuming a power-law CRe energy spectrum ranging from 0.5 MeV to 560 GeV,
      where the spectrum is space-independent,
      %Assuming a leptonic model with a spatially uniform, power-law CRe spectrum
      %ranging from 0.5 MeV to 562.1 GeV,
      we showed that the observed gamma-ray and microwave spectra

@@

\item The elapsed time of 12 Myr is required for the simulated bubbles
      to reach the desired morphology.

@@

\item The Galactic bubbles are observed nearly symmetric about the Galactic plane albeit\

@@

      which relieve the caveat of earlier jet models where jets need to be vertical.
